% Created 2018-06-27 Wen 03:45
\documentclass[letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
% <<< packages
\RequirePackage{latexsym,amsmath,amssymb,charter,color,calc,hyperref,titlesec}
\RequirePackage[empty]{fullpage}
% >>>

% <<< dimensions/margins
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\addtolength{\oddsidemargin}{-0.25in}
\addtolength{\evensidemargin}{-0.25in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}
% >>>

% <<< other definitions
\definecolor{my-gray}{gray}{0.90}
\definecolor{url-gray}{gray}{0.25}
% >>>

%% Document header
\newcommand{\resheader}[6]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}cr}
    #3 & \textbf{\LARGE #1} & #5\\
    #4 & \url{#2}           & #6\\
    \end{tabular*}
    \\
    \vspace{0.1in}
}

%% Enumerations
\def\labelitemi{--}

%% Section Headings, etc.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\section}[1]{
  {
    \large \colorbox{my-gray}{
      \begin{minipage}
        {\textwidth-0.175in}
        {\textbf{#1 \vphantom{p\^{E}}}}
      \end{minipage}
    }
  }
}

\titleformat{\subsection} %command
            [block] %shape
            {\bfseries} %format
            {} %label
            {0pt} %sep
            {} %before-code
            [] %after-code

\titlespacing{\subsection}{0pt}{5pt}{0pt}[{0pt}]

\titleformat{\subsubsection} %command
            [block] %shape
            {\vspace{-2.4ex}\small\it\raggedleft} %format
            {} %label
            {0pt} %sep
            {} %before-code
            [] %after-code
\titlespacing{\subsubsection}{0pt}{0pt}{0pt}[{0pt}]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand\maketitle{}
\hypersetup{colorlinks=true, urlcolor={url-gray}}
\usepackage{enumitem}
\setlist{leftmargin=0.25in,nosep}
\usepackage{multicol}
\date{}
\title{Igor\_Pogorelko}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 25.3.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle
% \resheader{ Igor Pogorelko }{ email:i.pogorelko@gmail.com }{ phone: 0974946856 }{ skype: i.pogorelko }{ Kharkiv }{ Ukraine }
{\LARGE Igor Pogorelko} \hfill {email: i.pogorelko@gmail.com}\\
\hfill {github: https://github.com/gruzchik}\\
\hfill {phone: 0974946856}\\
\hfill {skype: i.pogorelko}\\
\vspace*{1em plus .6em minus .5em}
\section{Personal statement}
\label{sec-1-1}
\\
Highly motivated specialist with more than 10 years of experience in IT. Good team-player easily acquiring new knowledge and grasping new technologies.\\
Result-oriented, proactive and responsible person. 
Substantial experience in system administration of Linux-based systems (Debian/Centos/Ubuntu/Gentoo) with special focus on Web and server infrastructure. Well-familiar with various CMS-systems , development, deployment , support  of websites, E-commerce engines and solutions.\\
\vspace*{1em plus .6em minus .5em}
Objective: Senior DevOps Engineer\\
\section{Expertise}
\label{sec-1-1}
\\
Hosting development, configuration and administration using webservers Tomcat, Apache and Nginx, deploying Web solutions to the hosting and various cloud platforms. Developing Bash and Python scripts for synchronizing of the system components , automation of wide scope of deployment and configuration tasks using Agile instruments: VCS(Git,SVN) Terraform and Jenkins.\\
Full development lifecycle support including requirements clarification and management, development, deployment and support of Web and E-commerce solutions based on Java, Node.js, PHP and Python. Database configuration and support using Mysql, MariaDB, PostgreSQL, MongoDB etc.\\
Hands-on experience supporting, automating and optimizing deployments to AWS and GCP, leveraging configuration management, CD/CD and DevOps processes.\\
\vspace*{1em plus .6em minus .5em}
Implementation solutions based on microservice architecture. Proficiency of creating and reconfiguration containers based on Docker, container orchestration systems like GKE and EKS
\section{Skills}
\label{sec-1}\\
\label{sec-1-1}
\textbf{Specialties:} Maintenance Engineer, Linux Administrator, Web developing, website and server scripting\\
\label{sec-1-2}
\textbf{Cloud Platforms:} GCP, AWS, DigitalOcean\\
\label{sec-1-3}
\textbf{Operations Systems:} Debian, CentOS, Ubuntu, Gentoo, openSUSE, Red Hat, FreeBSD, Fedora, Windows Server\\
\label{sec-1-4}
\textbf{Programming language:} Bash, Python, Mysql, Javascript, PHP, Java, HTML\\
\label{sec-1-5}
\textbf{Web Servers:} Apache, Nginx, Tomcat, lighttpd\\
\label{sec-1-6}
\textbf{Web CMS and frameworks:} Wordpress, Magento, Opencart, AEM, Django, Joomla, OsCommerce\\
\label{sec-1-7}
\textbf{Control Panels:} Cpanel, WHM, Plesk, Virtualmin\\
\label{sec-1-8}
\textbf{Databases:} Mysql, MariaDB, PostgreSQL, MongoDB\\
\label{sec-1-10}
\textbf{Virtualization:} KVM, Xen, VMware Workstation, OpenVZ, LXC\\
\label{sec-1-11}
\textbf{CI/CD and Build tools:} Jenkins, TeamCity, Gitlab Runner, ArgoCD, CloudBuild, Gradle, Maven\\
\label{sec-1-12}
\textbf{CCA tools:} Terraform, Ansible\\
\label{sec-1-13}
\textbf{Containers and microservices orchestration:} Docker, Kubernetes, Kustomize, Helm, Istio\\
\label{sec-1-14}
\textbf{VCS and tools:} Github, Gitlab, Bitbucket, SVN\\
\label{sec-1-15}
\textbf{Other skills:}  Node.js, iptables, LDAP, Bind, Nexus, Sonar, npm, Zabbix, Nagios, NFS, GlusterFS\\
\section{Work experience}
\label{sec-2}

\subsection{{August 2018 – Present}. DevOps Engineer, Epam Systems}
\label{sec-2-1}
\subsubsection{}
\label{sec-2-1-1}
\textbf{Project:} administration and automation of infrastructure\\
\textbf{Project Role:}  Deployment Engineer\\
\textbf{Responsibilities:}\\
\begin{itemize}
\item Creation, deployment and update infrastructure and services using Terraform and Ansible
\item Dev, Test and Stage environments implementation
\item Development of scripts using bash and python for server and infrastructure tasks, deploying them to hosts using Gitlab and Jenkins
\item Creating CI/CD process using Jenkins and Gitlab pipelines for Java and Node.js projects
\item Participation in Sprint and Kanban processes, resolving task and support developing team using Jira, Trello and other tools
\item SSL Certificates registration and implementation to the web services.
\item Organization and implementation of microservices , configuration of deployment to Google Kubernetes Engine
\end{itemize}
\textbf{Languages:} Bash, Python, SQL\\
\textbf{Technologies:} SSL, KVM, VPN\\
\textbf{Tools:} Kubernetes, Terraform, Jenkins, Ansible, Docker, Nginx, Jira, Zabbix, AWS CLI, Gcloud SDK \\ 
\textbf{Databases:} MongoDB, MySQL, MariaDB\\
\textbf{Source control tools:} Github, Bitbucket, Gitlab\\
\textbf{OS:} Debian, CentOS, Ubuntu, Amazon Linux \\
\subsection{{December 2010 – July 2018}. System Administrator of Hosting/Deployment Engineer, Datalink UK Ltd}
\label{sec-2-1}
\subsubsection{}
\label{sec-2-1-1}
\textbf{Project:} infrastructure administration and support Hosting Services for IT company\\
\textbf{Project Role:}  Server Administrator/Deployment Engineer\\
\textbf{Responsibilities:}\\
\begin{itemize}
\item Development of scripts using bash and python for server and infrastructure tasks, deploying them to hosts using Jenkins and Git
\item Optimization of the infrastructure deployment and automation of installing the necessary packages using Ansible, creating a simple playbooks and roles for installation backup system to the client host, monitoring, etc.
\item Creation and implementation of web solutions, servers infrastructure for  necessities of customers, migration the web commerce platforms.
\item Detection of SQL, XSS and other vulnerabilities on the compromised web sites, restoring and protection of website engines and web settings
\item Creation, deployment and support hosting accounts based on KVM, OpenVZ, LXC system.
\item Technical support of UK based customers via email, Skype and customer support system.
\item Management of DNS (Bind) and mail services(Postfix, Qmail, Exim), SVN, Docker, DHCP, VPN, etc.
\item Web sites development, OsCommerce, Typo3, Magento, upgrade the site functionality to the new versions of PHP, bug fixing.
\item SSL Certificates registration and deployment to the websites.
\end{itemize}
\textbf{Languages:} Bash, PHP, Python,  SQL\\
\textbf{Technologies:} SSL, KVM, XEN, VPN\\
\textbf{Tools:} Proxmox, Cpanel, Virtualmin, WHMCS, Ansible, Jenkins, Apache, Nginx, Zabbix, GlusterFS\\
\textbf{Databases:} MySQL, PostgreSQL\\
\textbf{Source control:} SVN, Git\\
\textbf{OS:} CentOS, Debian, Ubuntu, Redhat, FreeBSD\\
\subsection{July 2007 – November 2010. System Administrator/Web developer, Ametrin Co Ltd, Kharkiv, Ukraine.}
\label{sec-2-2}
\subsubsection{}
\label{sec-2-2-1}
\textbf{Project:} administration and support of IT infrastructure and Hosting Services\\
\textbf{Project Role:}  Server Administrator/Web developer\\
\textbf{Responsibilities:}\\
\begin{itemize}
\item Establishment and further development of the hosting server (apache2 mysql proftpd) (35 sites), as well as writing scripts to synchronize its work and automatic backup of content separately these resources (content and database mysql).
\item Creation, deployment and support of corporate and brand-oriented Web sites and blogs (over 15 Web sites) based on Joomla, WordPress, Slaed.
\item Creation, deployment and support of ecommerce solution based on Virtuemart with additional integration with 1C system for shop items import and update, adding statistics system and SEO for the e-shop. The shop has been put in operation and brings the company stable flow of about 100 orders a month with almost no initial investments in SEO.
\item Management of mail servers, Postfix Clamav Spamassasin, writing scripts in bash for solving production problems.
\item Management of DNS server BIND, and LDAP, SAMBA, DHCP, VPN, configuration and traffic distribution by using SQUID, the output statistics for users on the web via lightsquid.
\item Administration of local area networks and servers OS Linux Gentoo, routing, iptables, masquerading.
\item Set-up of services MRTG, logwatch, the registration system applications Mantis (database Postgres), the help system based on Mediawiki.
\item Administration of AD and Microsoft Exchange on Windows Server 2003.
\end{itemize}
\textbf{Languages:} Bash, PHP,  HTML, SQL\\
\textbf{Technologies:} DNS, LDAP, VPN\\
\textbf{Tools:}  Apache, Nginx, Squid, Mantis, Cacti\\
\textbf{Databases:} MySQL, PostgreSQL\\
\textbf{OS:} Gentoo, Debian, Windows Server 2003\\
\subsection{December 2004 – June 2007: Computer systems engineer, ISP Vokar Telecom, Kharkiv, Ukraine.}
\label{sec-2-4}
\subsubsection{}
\label{sec-2-4-1}
\textbf{Project:} ISP infrastructure support\\
\textbf{Project Role:}  Computer systems engineer.\\
\textbf{Responsibilities:}
\begin{itemize}
\item Creation of corporate Web-sites based on PhpNuke, Slaed, site support and customization.
\item Advising on configuration and use of software associated with the network and the Internet.
\item Administration Unix / Linux.
\item Assembly and maintenance of computer and office equipment.
\item Monitoring and remote work via ssh with routers, proxy, mail, Web and VPN-server on Linux.
\end{itemize}
\textbf{Languages:} Bash, PHP, HTML, SQL\\
\textbf{Technologies:} DNS, VPN\\
\textbf{Tools:}  Squid, Apache, Mysql, Postfix\\
\textbf{OS:} Centos, ASPLinux, FreeBSD, Windows 2000\\
%\section{Projects}
\section{Education}
\label{sec-4}
\subsection{Kharkivs'kij Nacional'nij Universytet Radioelectroniki, Kharkiv, Ukraine}
\label{sec-4-1}
Master degree in Electronics, Banking Systems Engineer, 1998-2003\\
\subsection{Kharkivs'kij Nacional'nij Universytet Radioelectroniki, Kharkiv, Ukraine}
\label{sec-4-1}
Master degree in Economics, Engineer Economist, 2003-2005\\
\subsection{Courses:}
\label{sec-4-1-2}
Professional Python Django courses in ITBursa, Kharkiv 2014-2015\\
L3 Linux high level. IT education center, Kiev 2016-2017\\
Architecting with Google Compute Engine, Coursera Certificate 2020\\
Architecting with Google Kubernetes Engine Specialization, Coursera Certificate 2020\\
\vspace*{1em plus .6em minus .5em}
\section{Additional Information}
\vspace*{1em}\\
\textbf{Languages:}  English(Upper Intermediate), Russian(Native), Ukrainian(Native), Polish(elementary)\\
\textbf{Driving License:} B Category\\
\textbf{Opportunity to work trips:} Foreign passport\\
% Emacs 25.3.1 (Org mode 8.2.10)
\end{document}
